Improved Bounds for Online Balanced Repartitioning

### 2020-03-28 paper/paper.tex
Figure description
Reduction not a LB

\title{Brief Announcement: Tight Bounds for Online Balanced Repartitioning}

@@

\section{Lower bound $2k-1$ for two clusters}

@@

\maciek{TODO: example figure of 3 sets split. Example figure of three states of OPT}

\begin{theorem}
  No deterministic algorithm for BRP with two clusters can achieve a competitive ratio smaller than $2k-1$.

  \maciek{better formulation below}
  Fix any $k$. If there exists a $\gamma$-competitive \ldots (SIDMA)
\end{theorem}

>>>>

\title{Improved Bounds for Online Balanced Repartitioning}

@@

\section{Dynamic Graph Bisection (two clusters case)}

\subsection{Lower bound $2k-1$}

@@

\maciek{TODO: figure of three states of OPT. It should fit next to the other lower bound figure?}

\begin{theorem}
  %No deterministic algorithm for BRP with two clusters can achieve a competitive ratio smaller than $2k-1$.

  Fix any $k$. If there exists a $\gamma$-competitive deterministic algorithm $B$ for Dynamic Bisection Problem with cluster size $k$, then there exists a $\gamma$-competitive deterministic algorithm $P$ for the paging problem with cache size $2k-1$ and where the number of different pages is $2k$. 
\end{theorem}
